---
title: "PreQuES-Land Use Change Trajectory Analysis"
format: 
   html:
     df-print: kable
toc: true
number-sections: true
editor: visual
editor_options: 
  chunk_output_type: console
execute:
  cache: false
engine: knitr
params:
  dir_traj_map_: "NA"
  dir_def_map_: "NA"
  dir_ques_pre_traj: "NA"
  dir_ques_pre_def: "NA"
---


```{r}
#| warning: false
#| echo: false
# key raster inputs: lc_t1_, lc_t2_, admin_
# key table inputs: lookup_traj_reclass, lookup_trajectory_complete
# key column inputs : trajectory and def
# key raster output: map_trajectory, map_deforest_degrad
library(terra)
library(dplyr)
library(LUMENSR)

traj_analysis_output <- 
  readRDS(params$dir_ques_pre_traj)

def_analysis_output <- 
    readRDS(params$dir_ques_pre_def)
```

# Analisis alur penggunaan lahan (FAO)

## Hasil analisis alur penggunaan lahan pada tingkat bentang lahan

### Peta kelompok perubahan penutupan lahan

```{r}
#| echo: false
#| warning: false
# Load the raster data for trajectory mapping from a given directory path
traj_map <- rast(params$dir_traj_map_)

# Perform a join operation between the categories of the trajectory map and the color lookup table
# The function color_landuse_trajectories() is presumed to return the color lookup table for trajectories
lookup_traj <-
  cats(traj_map)[[1]] |>  # Extract categories from the raster object 'traj_map'
  left_join(color_landuse_trajectories(),  # Join with the color lookup table
            by = "trajectory")  # Specify the common column 'trajectory' for the join operation

# Assign the joined color codes back to the levels of the raster object
levels(traj_map) <- lookup_traj

# Plot the categorical raster using a presumed function 'plot_categorical_raster()'
traj_map |> 
  plot_categorical_raster()  # Plot the raster data

```

### Intisari kelompok perubahan penutupan lahan

::: panel-tabset
#### Tabel

```{r}
#| echo: false
traj_analysis_output$landscape_level$table_traj_area
```

#### Grafik

```{r}
#| echo: false
traj_analysis_output$landscape_level$barplot_traj
```
:::

## Hasil analisis pada tingkat unit perencanaan

```{r}
#| echo: false
render_child <- function(results_list, i) {
  res = knitr::knit_child(
   text = xfun::read_utf8("quespretraj_by_pu.qmd"),
   envir = rlang::env(results_list = results_list, i = i),
   quiet = TRUE
  )
  cat(res, sep = '\n')
  cat("\n")
}
```

```{r}
#| results: "asis"
#| echo: false
for (i in names(traj_analysis_output[["pu_level"]])) {
  render_child(results_list = traj_analysis_output[["pu_level"]], i = i)
}
```

# Analisis alur penggunaan lahan (Deforestasi dan Degradasi)

## Hasil analisis alur penggunaan lahan pada tingkat bentang lahan

### Peta kelompok perubahan penutupan lahan

```{r}
#| echo: false
#| warning: false
def_map <- rast(params$dir_def_map_)
lookup_def <-
  cats(def_map)[[1]] %>%  # Extract categories from the raster object 'traj_map'
  left_join(color_forest_trajectories(),  # Join with the color lookup table
            by = "def")  # Specify the common column 'trajectory' for the join operation

# Assign the joined color codes back to the levels of the raster object
levels(def_map) <- lookup_def

def_map |> 
  plot_categorical_raster()
```

### Intisari kelompok perubahan penutupan lahan

::: panel-tabset
#### Tabel

```{r}
#| echo: false
def_analysis_output$landscape_level$table_traj_area
```

#### Grafik

```{r}
#| echo: false
def_analysis_output$landscape_level$barplot_traj
```
:::

## Hasil analisis pada tingkat unit perencanaan

```{r}
#| results: "asis"
#| echo: false
for (i in names(def_analysis_output[["pu_level"]])) {
  render_child(results_list = def_analysis_output[["pu_level"]], i = i)
}
```
